The Blue Obelisk five years on

### 2011-03-15 paper.tex
More on intro, plus suggestion on other areas of activity

The goals of the Blue Obelisk group were described in Guha et al.\cite{guha2006}. but are briefly summarised here...

@@

More recently, a number of workers have developed light-weight
toolkits that are targeted towards web applications. One example of
this form is the Chemdoodle library from XXX. The focus of these
toolkits is to support client-side cheminformatics functionality,
allowing for rich, chemically-aware browser-based applications.

@@

>>>>

The formation of the Blue Obelisk group is somewhat unusual in that it
is not a funded network, nor does it follow the industry consortium
model. Rather it is a grassroots organisation, catalysed by an initial
core of interested scientists, but with membership open to all who
share one or more of the goals of the group:
\begin{itemize}
\item Open Source. One can use other people's code without further permission, including changing it for one's own use and distributing it again.
\item Open Standards. One can find visible community mechanisms for protocols and communicating information. The mechanisms for creating and maintaining these standards cover a wide spectrum of human organizations, including various degrees of consent.
\item Open Data. One can obtain all data in the public domain when wanted and reuse it for whatever purpose.
\end{itemize}

The Blue Obelisk was first described in Guha et al.\cite{guha2006}. This
contribution looks back on the past 5 years and surveys progress and
remaining challenges in the areas of Open Source, Open Data and Open
Standards in chemistry.

@@

More recently, a number of workers have developed light-weight
toolkits that are targeted towards web applications. One example of
this form is the ChemDoodle library from iChemLabs. The focus of these
toolkits is to support client-side cheminformatics functionality,
allowing for rich, chemically-aware browser-based applications.

@@

\section*{Other areas of activity}
Web services? (NIH, CDK and Chemspider)

Books (Angel, Egon, OB)
